---
title: "Lab 2 Multiple Regression I"
author: "KSRM"
date: "2/14/2022"
output: html_document
---

Confidence in Submission: 70 
My response to the second problem is different from the solution code. I need to fix the learning trial labels using mapply. 
```{r setup, include=FALSE}
install.packages("knitr")
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2)
library(tibble)
```


The following changes have been made to figure 5.5 (pg 91/111:

- change to x-axis and y-axis titles 
- x-axis and y-axis ticks made the same
- implement different symbols to differentiate the lines 
```{r}
slamecka_design <- tibble(number_of_learning_trials = rep(c(2,4,8), each=6),
                          number_of_IL = rep(rep(c(2,4,8), 2), 3),
                          subjects = 1:18,
                          recall = c(35,21,6,
                                   39,31,8,
                                   40,34,18,
                                   52,42,26,
                                   61,58,46,
                                   73,66,52
                                   )
                          )
```



```{r}
slamecka_design$number_of_learning_trials = as.factor(slamecka_design$number_of_learning_trials )
ggplot(slamecka_design,aes(x = number_of_IL,
                           group = number_of_learning_trials,
                           y = recall, shape = number_of_learning_trials))+
  geom_line(stat = "summary", fun = "mean")+
  geom_point(stat = "summary", fun = "mean")+
  theme_classic()+
  theme(legend.position ="none")+
  scale_y_continuous(name = "Number of words correct", breaks = seq(0, 80, 20), limits = c(0,80))+
  scale_x_continuous(name = "Number of interpolated lists", breaks = c(2,4,8))+
  mapply(annotate, "text", x = 9, y = c(8,22,50), label = c("2 learning trials", "4 learning trials", "8 learning trials"))
```

Use R to create a dataframe to represent predictions for this new 3x3x3 design. Then use ggplot and facet wrapping to show predicted means for each condition.

```{r}

slamecka_design <- tibble(number_of_learning_trials = rep(c(2,4,8), each=6),
                          number_of_IL = rep(rep(c(2,4,8), 2), 3),
                          subjects = 1:18,
                          recall = c(35,21,6,
                                   39,31,8,
                                   40,34,18,
                                   52,42,26,
                                   61,58,46,
                                   73,66,52
                                   )
                          )

new_data <- tibble(reward = rep(c("0", "50", "1000000"), each = 9),
                   practice = rep(rep(c(2,4,8), each = 3),3),
                   number_of_IL  = as.factor(rep(c(0,4,8),9)),
                   recall = c(5,3,1,
                              6,4,2,
                              7,5,3,
                              10,8,6,
                              11,9,7,
                              12,10,8,
                              15,13,11,
                              16,14,12,
                              17,15,13
                              )
                   )

ggplot(new_data,aes(x=practice,
                    group = number_of_IL,
                    y=recall,
                    shape=number_of_IL))+
  geom_line()+
  geom_point()+
  theme_classic()+
  scale_y_continuous(name = "Number of words correct", breaks=c(0,5,10,15,20), limits=c(0,20))+
  scale_x_continuous(name = "Number of learning trials", breaks=c(2,4,8))+
  facet_wrap(~reward)
```

